Declarative Deployment Reconfiguration of Pulverised Collective Adaptive Systems at Runtime \thanks{ This work has been supported by the Italian PRIN Project COMMON-WEARS (2020HCWWLP) and the EU/MUR FSE REACT-EU PON R\&I 2014-2020. }

### 2023-05-21 paper-2023-acsos-pulverization.tex
Minors on bib

The general solution is to devise 
 a reasonable partitioning of the software system
 and a corresponding (dynamic) deployment plan 
 defining the mapping between the software components and the target deployment domain~\cite{DBLP:journals/jss/ArcangeliBL15}.
%
In the context of \acp{cas},
 previous work proposes an application partitioning schema,
 called \emph{pulverisation}~\cite{FI2020-pulverization},
 the fosters the decoupling of business logic and deployment concerns.
%
In short, the core idea is to consider devices as \emph{logical} entities,
whose software can be designed as (or broken down to, if already existing) an ensemble of \emph{five components
(behaviour, state, communication, sensors, and actuators)}
 that can be deployed with flexibility on available infrastructure without (ideally) affecting application functionality. %whose actual host can be decided at deployment time.
%
This way, the designer can focus on the business logic at hand,
delaying an optimised deployment to later stages of the sofware design,
thus gaining resilience to changes in the infrastructure or in non-functional requirements.
%
One limitation of previous work on pulverisation regards dynamicity:
although the application can be deployed on arbitrary systems,
there is no support for the reconfiguration of components at runtime, as a reaction to changing conditions or requirements.

>>>>

The general solution is to devise 
 a reasonable \emph{partitioning}~\cite{DBLP:journals/jnca/LiuASGBQ15} of the software system
 and a corresponding (dynamic) deployment plan 
 defining the mapping between the software components and the target deployment domain~\cite{DBLP:journals/jss/ArcangeliBL15}.
%
In the context of \acp{cas},
 previous work proposes an application partitioning schema,
 called \emph{pulverisation}~\cite{FI2020-pulverization},
 the fosters the decoupling of business logic and deployment concerns.
%
In short, the core idea is to consider devices as \emph{logical} entities,
whose software can be designed as (or broken down to, if already existing) an ensemble of \emph{five components
(behaviour, state, communication, sensors, and actuators)}
 that can be deployed with flexibility on available infrastructure without (ideally) affecting application functionality. %whose actual host can be decided at deployment time.
%
This way, the designer can focus on the business logic at hand,
delaying an optimised deployment to later stages of the sofware design,
thus gaining resilience to changes in the infrastructure or in non-functional requirements.
%
One limitation of previous work on pulverisation regards dynamicity:
although the application can be deployed on arbitrary systems,
there is no support for the reconfiguration of components at runtime, as a reaction to changing conditions or requirements.
